\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-25 paper.tex
Update results

% The following packages can be found on http:\\www.ctan.org
\usepackage{caption}
\usepackage{color}
\usepackage{graphicx} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algpseudocode}  %\usepackage[noend]{algpseudocode}
\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{proof}
\newtheorem{property}{Property}
\usepackage[numbers]{natbib}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
\algnewcommand\algorithmicoutput{\textbf{Output:}}
\algnewcommand\OUTPUT{\item[\algorithmicoutput]}
\makeatletter
\makeatother
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}

@@

\textcolor{blue}{
The main difficulty is to handle 
the scalar parameter $\alpha$ determining how much of the computed step  will be traveled along. 
As presented in Algorithm~\ref{algo:gradient}, $\alpha$ takes two values, $\alpha_{init}<1$ to process smaller steps or $1$ to go directly to the optimum. This latter case is interesting since, if this optimal path is collision-free, the algorithm has converged and returns the path as the solution.
Choosing to travel small steps from a valid path decrease the chances of being in collision. Besides if one occurs, the collision-constraint is computed on the last valid path, which is not too much deformed compared to the path that has collisions. As a result, collision-constraints are only computed (\texttt{computeCollisionConstraint}) and added (\texttt{addCollisionConstraint}) when performing a reduced iteration (i.e. $\alpha = \alpha_{init}$).
}

@@

\subsubsection{Analysis of $\alpha_{init}$ influence}
\textcolor{blue}{Results without comparison to RS and PRS here
$\alpha_{init}$ could be computed from geometrical considerations.
}
TODO !!

\begin{figure}[H]
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{2Darm_comparison_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:double_arm}
	}
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{2Darm_comparison_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:double_arm}
	}
  \caption{Influence of $\alpha_{init}$.}
  \label{fig:remainingLengthAlphaInit}
\end{figure}

@@

We also experiment our algorithm on more complex robots and environments.
In the included video and Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}, we present multiple situations where the GB algorithm 
is tested and compared to RS~\cite{randomShortcutHPP}
Algorithm~\ref{algo:random-shortcut} and PRS~\cite{partialrandomShortcutHPP} 
adapted from~\cite{GeraertsIJRR07}.
\textcolor{blue}{
The termination condition of RS allows it to try 
shortening the path until the optimization duration overflows a time limit. 
This corresponds to $t_{lim}$ in Algorithm~\ref{algo:random-shortcut} and is typically equal to the Gradient-Based optimization duration.
%For our implementation of PRS, first a shortcut is tried on each DOF between $\conf_0$ and $\conf_{wp+1}$. % NOT ANYMORE
The implementation of PRS is identical to~\cite{GeraertsIJRR07}:
for a random DOF, configurations are sampled as in 
Algorithm~\ref{algo:random-shortcut}. The steering-method returns a path made of 
an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, we replace it as in RS. As RS, the process is stopped when the duration exceeds $t_{lim}$.
}

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to Figure~\ref{fig:trajectories:puzzle}. The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
Lengths of initial, GB optimized, and RS optimized paths are 
respectively 23.4, 8.53 and 10.2. PRS fails to decrease the path length because in 
this problem, all DOF are closely related to cross the hole. This behavior was also 
noticed and improved in the PRS implementation of~\cite{GeraertsIJRR07}, 
acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory 
even in the hole, contrary to RS which simply copies the initial path when the 
trajectory gets near of the obstacle. $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.

@@

% double-arm:
In the double-arm situation, Figure~\ref{fig:trajectories:double_arm}, one arm has 
to get around a cylinder obstacle while the 
other arm is relatively far from obstacles. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Unlike RS, 
the GB optimizer manages to cancel the rotation of the free-arm while optimizing the 
first arm motion, even if the second arm is still moving because of the translation 
motion. The initial path length 5.17 is decreased to 4.55 by RS, to 4.06 by PRS and 
to 2.77 by the GB method using three collision-constraints with the cylinder obstacle.

@@

% UR5-spheres:
Some problems are 
involving a 6-axis manipulator arm, also called UR5, equipped with a bar or a 
gripper.
In a relatively free environment represented in Figure~\ref{fig:trajectories:ur5}, 
results from our method and RS are similar (path length are respectively 2.03 and 1.60). 
Note also that the end-effector trajectory is completely different from the initial 
one: the robot is easily passing between the spheres, keeping its end-effector 
above.

% UR5-fiad
For an UR5 working in a cluttered environment inspired by an industrial issue 
Figure~\ref{fiad}, path optimization efficiently returns a shorter solution, close 
to the result of RS and to what can be observed in reality~\cite{factory-day-video}. 
The initial path length 6.65 is decreased to 2.08 by RS, to 
1.98 by the GB optimizer and unchanged by PRS.

% baxter:
A problem involving a Baxter-like\footnote{A torso rotation was added.} robot 
manipulating in an office environment is presented in
Figure~\ref{fig:trajectories:baxter}. The robot starts with its end-effectors 
above the computer and has to 
turn and reach the shelf. According to the left-hand trajectories quality (see the 
video for the full motion) and path lengths, 9.10 (initial RRT-connect), 7.52 (RS), 
8.41 (PRS) and 2.70 (GB), the GB optimizer is the most successful in this case.

@@

% analysis PR2 alone:
In the example shown Figure~\ref{pr2_final} and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one, without any assumption about the group of DOF to activate (i.e. no DOF is locked). 
The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on the ground. Such behavior induces a high initial path length 
30.6. RS hardly optimizes the mobile base 
translation (Figure~\ref{pr2_final} middle) of the robot and other unnecessary DOF 
uses, resulting in a path length of 4.08.
Whereas the GB optimized-path mainly 
results in moving the arms as expected (Figure~\ref{pr2_final} right), just creating 
two collision-constraints between the arms. In the PRS 
result, only presented in the video, the mobile base motion is canceled. However, this is \textcolor{blue}{not} the case for other unnecessary DOF motions. In addition, the arms motion is very wide and not as optimized as in the GB trajectory.

% analysis PR2 in kitchen:
We obtain similar results on the PR2 performing manipulation tasks 
in a kitchen environment.
Firstly, the robot moves its hands from the top to the bottom of a table.
The different trajectories of the right gripper are indicated in Figure~\ref{fig:trajectories:kitchen1}.
Our optimizer manages to reduce the initial path length 12.7 from visibility-PRM 
and improves the path quality 
just adding constraints between the table and the 
robot's arms. Thus, the robot just slightly moves 
backward and uses its arms DOF to avoid the table, instead of 
processing a large motion to get away from the table. With the GB algorithm, the path length is 
reduced to 3.15, against 5.47 for RS.
Secondly, another example of PR2 going from the set to the fridge 
door is presented Figure~\ref{fig:trajectories:kitchen2} with the mobile base
trajectories. Here, GB and RS results are similar in terms of length and rendering.

@@

\begin{figure}[H]
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_comparison_RS_PRS_GB_sd.png}
		\label{fig:remainingLengthComp:double_arm}
	}
	\subfigure[PR2-crossing-arms]{
		\includegraphics[width=6.5cm,height=5.5cm]{PR2alone_comparison_RS_PRS_GB_sd.png}
		\label{fig:remainingLengthComp:pr2alone}
	}
  \caption{Performance comparison between the three optimizers.}
  \label{fig:remainingLength}
\end{figure}

Optimization computation time and path length averages are presented for 30 runs of 
each example in (Table~\ref{tab:results}). In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case. 
On the one hand, for non-high DOF examples, it appears that computation time is higher using the GB 
optimization. The worst case comes out for the puzzle problem where the number of 
constraints of GB is significant and $\alpha_{init}$ reduced. 
In addition, collision checking is rapidly processed in such basic problem geometry. This favors RS while the GB optimizer spends time on the \textcolor{blue}{LC}QP resolution to avoid collisions.
On the other hand, our method almost always provides the shortest paths, whereas it 
is not even the best criterion to quantify the parasite motions disappearance.
Note that these results are the consequence of the termination conditions of RS and PRS, balancing length reduction or shorter computation time. 
This is particularly visible for PRS which 
easily gives up in some problems, such as the 2D sliding-robot, the 
UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of (Table~\ref{tab:results}). 
Thus the issue addressed in Figure~\ref{decoupled_DOF_optimization} is 
solved considering this DOF.

@@

\begin{figure}
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_orth_constr_results.png}
		\label{fig:trajectories:double_arm}
	}
	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=6.5cm,height=5.5cm]{puzzle_orth_constr_results.png}
		\label{fig:trajectories:puzzle}
	}
	\subfigure[PR2-in-kitchen-1]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2-kitchen1_orth_constr_results.png}
		\label{fig:trajectories:kitchen1}
	}
	\subfigure[UR5-with-spheres]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur5-spheres_orth_constr_results.png}
		\label{fig:trajectories:ur5}
	}
	\subfigure[PR2-in-kitchen-2]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2_kitchen2_orth_constr_results.png}
		\label{fig:trajectories:kitchen2}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=6.5cm,height=5.5cm]{baxter_orth_constr_results.png}
		\label{fig:trajectories:baxter}
	}
  \caption{Trajectories of end-effectors, mobile bases or centers along the 
  different paths: the initial path is represented in red, the RS optimized path in 
  blue and the GB optimized path in green. The full robots 
  motions can also be visualized in the joined video. The trajectories comparison 
  highlights the optimization success of our method, which manages to deliver a 
  shorter or similar path compared to RS output.}
  \label{fig:trajectories}
\end{figure}

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $21.9$  &\\
    \textbf{2D slidding-robot} & GB & $9.29\,\text{ms}$ & $17.0$  &\\
    \textbf{(Fig.~\ref{2D_long} right)} & PRS & $0.336\,\text{ms}$ & $21.7$  &\\
    & RS & $1.89\,\text{ms}$ & $17.7$  &\\
    \midrule
    & Initial &  & $18.8$  &\\
    \textbf{Freeflyer-} & GB ($\alpha_{init}=0.05$) & $1020\,\text{ms}$ & $9.65$  &\\
    \textbf{puzzle} & PRS & $1.13\,\text{ms}$ & $18.8$  &\\
    & RS & $4.72\,\text{ms}$ & $10.3$  &\\
    \midrule
    & Initial &  & $10.8$  &\\
    \textbf{Double-arm} & GB & $10.3\,\text{ms}$ & $4.79$  &\\
    \textbf{5-DOF} & PRS & $2.17\,\text{ms}$ & $8.08$  &\\
    & RS & $5.33\,\text{ms}$ & $6.24$  &\\
    \midrule
    & Initial (RRT) &  & $4.97$ &\\
    \textbf{UR5-} & GB ($\alpha_{init}=0.4$) & $2.12\,\text{s}$ & $2.97$ &\\
    \textbf{with-spheres} & PRS & $0.884\,\text{s}$ & $4.56$ &\\
    & RS & $2.89\,\text{s}$ & $2.99$ &\\
    \midrule
    & Initial &  & $4.83$ &\\
    \textbf{UR5-} & GB ($\alpha_{init}=0.4$) & $314\,\text{ms}$ & $2.25$ &\\
    \textbf{industrial-example} & PRS & $30.2\,\text{ms}$ & $4.53$ &\\
    & RS &  $95.6\,\text{ms}$ & $2.16$ &\\
    \midrule
    & Initial &  & $20.2$ &\\
    \textbf{Baxter-in-} & GB & $22.7\,\text{s}$ & $6.65$ &\\
    \textbf{office} & PRS & $9.49\,\text{s}$ & $18.9$ &\\
    & RS & $3.13\,\text{s}$ & $11.9$ &\\
    \midrule
    & Initial &  & $12.6$  & $9.57$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $1.28\,\text{s}$ & $2.57$  & $0\,\text{m}$\\
    \textbf{arms} & PRS & $2.63\,\text{s}$ & $ 5.31$ & $0\,\text{m}$\\
    & RS & $1.92\,\text{s}$ & $3.59$ & $2.63\,\text{m}$\\
    \midrule
    & Initial &  & $15.3$ &\\
    \textbf{PR2-in-} & GB & $19.2\,\text{s}$ & $4.53$ &\\
    \textbf{kitchen-1} & PRS & $23.5\,\text{s}$ & $12.2$ &\\
    & RS & $9.88\,\text{s}$ & $5.75$ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper and 
in the video. For each run, a solution path is planned by Visibility-PRM (unless 
`RRT' for RRT-connect is mentioned) as initial guess for each optimizer.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

>>>>

% The following packages can be found on http:\\www.ctan.org
\usepackage{caption}
\usepackage{color}
\usepackage{graphicx} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algpseudocode}  %\usepackage[noend]{algpseudocode}
\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{proof}
\newtheorem{property}{Property}
\usepackage[numbers]{natbib}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
\algnewcommand\algorithmicoutput{\textbf{Output:}}
\algnewcommand\OUTPUT{\item[\algorithmicoutput]}
\makeatletter
\makeatother
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\usepackage{minibox}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

@@

\textcolor{blue}{
One main difficulty is to handle 
the scalar parameter $\alpha$ determining how much of the computed step  will be traveled along. 
As presented in Algorithm~\ref{algo:gradient}, $\alpha$ takes two values, $\alpha_{init}<1$ to process smaller steps or $1$ to go directly to the optimum. This latter case is interesting since, if this optimal path is collision-free, the algorithm has converged and returns the path as the solution.
Choosing to travel small steps from a valid path decrease the chances of being in collision. Besides if one occurs, the collision-constraint is computed on the last valid path, which is not too much deformed compared to the path that has collisions. As a result, collision-constraints are only computed (\texttt{computeCollisionConstraint}) and added (\texttt{addCollisionConstraint}) when performing a reduced iteration (i.e. $\alpha = \alpha_{init}$).
}

@@

@@

Our algorithm is also experimented on more complex robots and environments.
In the included video and Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}, we present multiple situations where the GB algorithm 
is tested and compared to RS  and PRS.
\textcolor{blue}{
After describing the random optimizers, we will present each benchmark and its qualitative path results. Then quantitative averages and graphs will be given and discussed.
}

\textcolor{blue}{
The RS (see Algorithm~\ref{algo:random-shortcut}) shortens the path by randomly sampling configurations along it and trying to link them with collision-free interpolations.
The termination condition of RS is a duration time limit $t_{lim}$, and is typically set as the GB optimization duration.
%For our implementation of PRS, first a shortcut is tried on each DOF between $\conf_0$ and $\conf_{wp+1}$. % NOT ANYMORE
The implementation of PRS is identical to~\cite{GeraertsIJRR07}:
for a random DOF, configurations are sampled along the initial path as in 
Algorithm~\ref{algo:random-shortcut}. The steering-method returns a path 
made of an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, it is added to the final path as in RS. The process is stopped when the duration exceeds $t_{lim}$.
}

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to Figure~\ref{fig:trajectories:puzzle}. The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
The GB optimizer manages to modify the puzzle trajectory even in the hole, but remains less efficient than RS and PRS. We explain this behavior by the fact that, ........
%PRS fails to decrease the path length because in this problem, all DOF are closely related to cross the hole. This behavior was also noticed and improved in the PRS implementation of~\cite{GeraertsIJRR07}, acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory even in the hole, contrary to RS which simply copies the initial path when the trajectory gets near of the obstacle.

@@

% double-arm:
In the double-arm benchmark (4-DOF), 
Figure~\ref{fig:trajectories:double_arm}, one arm has 
to get around a cylinder obstacle while the 
other arm stay in the same configuration. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Unlike RS, 
the GB optimizer manages to cancel the rotation of the free-arm while optimizing 
the first arm motion, creating collision-constraints with the cylinder obstacle.

@@

% UR5-spheres and fiad:
Some problems are 
involving a 6-axis manipulator arm, also called UR5, equipped with a bar or a 
gripper.
In a relatively free environment represented in Figure~\ref{fig:trajectories:ur5}, 
results from our method and RS are similar. 
Note also that the end-effector trajectory is completely different from the initial 
one: the robot is easily passing between the spheres, keeping its end-effector 
above.
For an UR5 working in a cluttered environment inspired by an industrial issue 
Figure~\ref{fiad}, path optimization efficiently returns a shorter solution, close 
to the result of RS and to what can be observed in 
reality~\cite{factory-day-video}.

% baxter:
A problem involving a Baxter-like\footnote{A torso rotation was added and 
the grippers were removed.} robot 
manipulating in an office environment is presented in
Figure~\ref{fig:trajectoriesbis:baxter}. The robot starts with its end-effectors 
above the computer and has to 
turn and reach the shelf. According to the left-hand trajectories quality (see the 
video for the full motion) and path lengths, the GB optimizer provides 
the smoothest motion.

@@

% analysis PR2 alone:
In the example shown Figure~\ref{pr2_final} and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one, without any assumption about the group of DOF to activate (i.e. no DOF is locked). 
The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on the ground. Such behavior induces a high initial path length. RS hardly optimizes the mobile base 
translation (Figure~\ref{pr2_final} middle) of the robot and other unnecessary DOF 
uses. Whereas the GB optimized-path mainly 
results in moving the arms as expected (Figure~\ref{pr2_final} right), just creating two collision-constraints between the arms. 
\textcolor{blue}{
In the PRS result, only presented in the video, the motion is less optimized than with RS: the arms are moving widely and the mobile base remains activated. One solution to remove such unnecessary DOF activation can be to try applying a partial shortcut on each DOF between the initial and final configuration. It appears that this step is more costly in terms of computation time than the GB duration, therefore it cannot be afforded by our PRS implementation. However, it could be applied as a preliminary optimization for each optimizer.
}

% analysis PR2 in kitchen:
Similar results are obtained on the PR2 performing manipulation tasks 
in a kitchen environment.
Firstly, the robot moves its hands from the top to the bottom of a table.
The different trajectories of the right gripper are indicated in Figure~\ref{fig:trajectoriesbis:kitchen1}.
Our optimizer manages to reduce the initial path length from visibility-PRM 
and improves the path quality 
just adding constraints between the table and the 
robot's arms. Thus, the robot just slightly moves 
backward and uses its arms DOF to avoid the table, instead of 
processing a large motion to get away from the table.
Secondly, another example of PR2 going from the set to the fridge 
door is presented Figure~\ref{fig:trajectoriesbis:kitchen2} with the mobile base
trajectories. Here, GB and RS results are similar in terms of length and rendering.

@@

\textcolor{blue}{
For some of the presented benchmarks, convergence graphs of the path 
length reduction are 
given Figure~\ref{fig:remainingLength}. The chosen initial paths are unchanged, 
e.g. correspond to Figures~\ref{fig:trajectories} and~\ref{fig:trajectoriesbis} . 
Each graph illustrates the percent ratio of the optimized path length over the initial path length, during the optimization time.
For the random optimizers curves, averages and standard deviations on 50 
launches are given. It is not a surprise that GB is globally slower than RS which converges faster. 
}

\begin{table}
\renewcommand{\arraystretch}{1.3}
\centering
\scalebox{0.9}{
  \begin{tabular}{cccC{1.3cm}C{1.3cm}C{1.3cm}}
  \toprule
  \multirow{2}{*}{\textbf{Problem}} &  & \multirow{2}{*}{Computation time} & \multicolumn{3}{c}{\minibox{Relative remaining length (\%)}} \\
   & & &  GB  &  RS  &  PRS  \\
  \midrule
  \midrule
  %\textbf{2D slidding-robot (Fig.~\ref{2D_long} right)} & & 11.9 ms & 78.3 & 68.0 & 81.8 \\
  \textbf{Freeflyer-puzzle} & ($\alpha_{init}=0.1$) & 0 ms & 0 & 0 & 0 \\
  \textbf{Double-arm 4-DOF} & & 39.6 ms & 46.8 & 55.5 & 63.5 \\
  \textbf{UR5-with-spheres} & (RRT, $\alpha_{init}=0.3$) & 3.18 s & 53.8 & 47.5 & 67.8 \\
  \textbf{UR5-industrial-example} & (RRT) & 0 ms & 0 & 0 & 0 \\
  \textbf{Baxter-in-office} & & 0 ms & 0 & 0 & 0 \\
  \textbf{PR2-crossing-arms} & & 882 ms & 19.9 & 43.2 & 95.2 \\
  \textbf{PR2-in-kitchen-1} & & 0 ms & 0 & 0 & 0 \\
  \bottomrule
  \end{tabular}  }%scalebox
\caption{Average results for 50 runs of several examples presented in the 
paper. For each run, a solution path is planned by Visibility-PRM 
(unless `RRT' for RRT-connect is mentioned) as initial guess for the 
three optimizers. The RS and PRS results correspond to averages of 50 
launches of the random optimizers on each initial guess. The GB 
computation time is the work duration allowed for the random optimizers. 
$\alpha_{init}=0.2$ unless another value is specified.
%For the PR2-crossing-arms example only, the right column represents the distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

\textcolor{blue}{
Since the GB optimizer results depend on the shape of the initial guess, e.g. the number of waypoints and the proximity to obstacles, results averages for 50 initial paths of each benchmark are presented in Table~\ref{tab:results}. As mentioned, the paths are obtained from Visibility-PRM or RRT-connect. Due to their nature, these motion planners provide different types of path: the output of Visibility-PRM contains less waypoints and does not tend to be close to the contact, behavior induced by the extension process of RRT.
}

In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case.
\textcolor{blue}{
The following section deals with the $\alpha_{init}$ influence in depth.
}
Except the low-DOF problem of the puzzle, our method almost always provides the 
shortest paths, whereas it is not even the best criterion to quantify the parasite 
motions disappearance.
TO COMPLETE!
%Finally, the complete vanishing of the mobile base motion in the GB optimized path is noted. 
%Thus the issue addressed in Figure~\ref{decoupled_DOF_optimization} is solved considering this DOF.

\subsubsection{Analysis of $\alpha_{init}$ influence}
\textcolor{blue}{Results without comparison to RS and PRS here
$\alpha_{init}$ could be computed from geometrical considerations.
}
TODO !!
Contrary to a first idea that $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.

\begin{figure}[H]
	\centering
	\subfigure[2D slidding-robot (Fig.~\ref{2D_long} right)]{
		\includegraphics[width=6.8cm,height=5.5cm]{potential2D_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:2Drobot}
	}
	\subfigure[Double-arm]{
		\includegraphics[width=6.8cm,height=5.5cm]{ur2_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:double_arm}
	}
  	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=6.8cm,height=5.5cm]{puzzle_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:puzzle}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=6.8cm,height=5.5cm]{baxter_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:baxter}
	}
  \caption{Influence of $\alpha_{init}$ on the convergence graphs of the GB optimizer.}
  \label{fig:remainingLengthAlphaInit}
\end{figure}

@@

\begin{figure}
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=2.9cm,height=5.5cm]{ur2_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_traj.png}
		\label{fig:trajectories:double_arm}
	}
	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=2.9cm,height=5.5cm]{puzzle_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{puzzle_traj.png}
		\label{fig:trajectories:puzzle}
	}
	\subfigure[UR5-with-spheres]{
		\includegraphics[width=2.9cm,height=5.5cm]{ur5spheres_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{ur5spheres_traj.png}
		\label{fig:trajectories:ur5}
	}
  \caption{(Left) Initial and final configurations.
  (Right) Trajectories of end-effectors or centers along the 
  different paths: the initial path is represented in red, the RS 
  output in blue, the PRS output in cyan (top only) and the GB optimized path 
  in green. The full robots 
  motions can also be visualized in the joined video. The 
  trajectories comparison highlights the optimization success of our method, 
  which manages to deliver a shorter or similar path compared to the RS output. 
  GB also cancels unecessary DOF activation contrary to RS and PRS (see the 
  lower arm in top-right Figure).}
  \label{fig:trajectories}
\end{figure}

\begin{figure}
	\centering
	\subfigure[PR2-in-kitchen-1]{
		\includegraphics[width=2.9cm,height=5.5cm]{pr2kitchen1_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{pr2kitchen1_traj.png}
		\label{fig:trajectoriesbis:kitchen1}
	}
	\subfigure[PR2-in-kitchen-2]{
		\includegraphics[width=2.9cm,height=5.5cm]{pr2kitchen2_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{pr2kitchen2_traj.png}
		\label{fig:trajectoriesbis:kitchen2}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=2.9cm,height=5.5cm]{baxter_initfinal.png}
		\includegraphics[width=6.5cm,height=5.5cm]{baxter_traj.png}
		\label{fig:trajectoriesbis:baxter}
	}
  \caption{Other trajectories comparisons of end-effectors or mobile bases (initial path in red, RS output in blue and GB output in green).}
  \label{fig:trajectoriesbis}
\end{figure}

\begin{figure}
	\centering
	\subfigure[2D sliding robot (Fig.~\ref{2D_long})]{
		\includegraphics[width=6.5cm,height=5.5cm]{potential2D_comp.png}
		\label{fig:remainingLengthComp:potential2D}
	}
	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=6.5cm,height=5.5cm]{puzzle_comp.png}
		\label{fig:remainingLengthComp:puzzle}
	}
	\subfigure[UR5-with-spheres]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur5spheres_comp.png}
		\label{fig:remainingLengthComp:ur5sphere}
	}
	\subfigure[PR2-crossing-arms]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2crossing_comp_prune.png}
		\label{fig:remainingLengthComp:pr2alone}
	}
	\subfigure[PR2-in-kitchen-1]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2kitchen1_comp.png}
		\label{fig:remainingLengthComp:pr2kitchen1}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=6.5cm,height=5.5cm]{baxter_comp_prune.png}
		\label{fig:remainingLengthComp:baxter}
	}
  \caption{Convergence graphs of the three optimizers during the optimization process. For each benchmark, the considered intial paths correspond to the ones of Figures~\ref{fig:trajectories} and~\ref{fig:trajectoriesbis}. The remaining path length relative to the initial one is represented. The dashed blue line is the final result of GB. For RS and PRS, the averages and standard deviations (in grey) over 50 launches are plotted.}
  \label{fig:remainingLength}
\end{figure}
